Improving the Image Acquisition Rate \\ of an Atomic Force Microscope \\ Through Sub-sampling and Reconstruction

### 2019-06-27 latex/coverletter.tex
Add sponsors to coverletter.

\documentclass[a4paper,twoside]{article}
\usepackage[margin=1in]{geometry}
\begin{document}
\hspace*{0.45\linewidth}
\begin{minipage}{0.52\linewidth}
Roger A. Braker\par
University of Colorado, Boulder\par
Dept of Electrical, Computer and Energy Engineering \par
425 UCB\par
Boulder, CO 80305\par
United States\par
roger.braker@colorado.edu\par
\today
\end{minipage}
\par\bigskip

@@

It is our pleasure to submit this manuscript entitled ``Improving the Image Acquisition Rate of an Atomic Force Microscope Through Sub-sampling and Reconstruction'' (authored by Roger A. Braker Yufan Luo, Lucy Y. Pao and Sean Andersson) for consideration to be published in the Transactions on Mechatronics. This paper is submitted for possible publication in the Focused Section on Nano/Micro 
Motion  Systems:  Design,  Sensing  and  Control(NMMS).

>>>>

\documentclass[a4paper,twoside]{article}
\usepackage[margin=1.5in]{geometry}
\begin{document}
\hspace*{0.45\linewidth}
\begin{minipage}{0.52\linewidth}
Roger A. Braker\par
University of Colorado, Boulder\par
Dept of Electrical, Computer and Energy Engineering \par
425 UCB\par
Boulder, CO 80305\par
United States\par
roger.braker@colorado.edu\par
\today
\end{minipage}
\par\bigskip

@@

It is our pleasure to submit this manuscript entitled \textit{Improving the Image Acquisition Rate of an Atomic Force Microscope Through Sub-sampling and Reconstruction} (authored by Roger A. Braker Yufan Luo, Lucy Y. Pao and Sean Andersson) for consideration to be published in the Transactions on Mechatronics. This paper is submitted for possible publication in the Focused Section on Nano/Micro 
Motion  Systems:  Design,  Sensing  and  Control(NMMS).

While sub-sampling schemes have seen increased attention recently, many of the existing studies are based purely on simulation. In contrast, this manuscript largely focuses on the experimental challenges which must be overcome to realize a sub-sampling scheme.

The manuscript has not been published nor is it under review elsewhere. All four authors agree to submit the manuscript in its present form to the IEEE/ASME Transactions Mechatronics focused section NMMS. This work was supported in part by Agilent Technologies, Inc, The US National Science Foundation (under Grants CMMI-1234980, CMMI-1234845, CMMI-1562031, and DBI-1352729), and the Hanse Wissenschaftskolleg in Delmenhorst, Germany. Thank you for the consideration and we look forward to hearing from you.
